\documentclass[a4paper,english,10pt]{book}

\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[pdftex]{graphicx}
\usepackage[english]{babel}
\usepackage{times}
\usepackage{multirow}
\usepackage[latex2html,backref,pdftitle={GOsa}]{hyperref}
\usepackage{html,color}
\usepackage{latexsym}
\usepackage{anysize}
\usepackage{float}
\usepackage{longtable}
\usepackage{verbatim}

\author{Alejandro Escanero Blanco}
\title{System Management with GOsa }
\date{28-03-05}

\marginsize{3cm}{2cm}{2.5cm}{2.5cm}


\begin{document}

\maketitle
\newpage
\tableofcontents
\newpage
\listoffigures
\newpage
\listoftables
\newpage

\chapter*{Preamble}

\htmladdnormallink{GOsa}{http://gosa.gonicus.de}, was a project created in year 2001 by Cajus Pollmeier \htmladdnormallink{Cajus Pollmeier}{mailto://pollmeier@gonicus.de}

In the 1.0 version GOsa was a an ambitious project, but badly focused. I entred as developer of the project in June of 2003 for the early versions of the branch 1.99.xx.
The code was remade from scratch, and we created a new modular and extensible version (based on plugins) and optimizing its operations enormously.

The actual version of GOsa (in the date of this document) is 2.3.
It have the ability to manage a great amount of services like samba2/3, pureftpd, postfix, cyrus-imap, posix, etc.
It have a small but very active developer group directed by Cajus.

\chapter{Introduction}
The management of systems can be a really complicated work, too many users with diferents services and access to them.

\section{Copyright and Disclaimer}
Copyright (c) 2005 Alejandro Escanero Blanco. Permission is granted to copy, distribute and/or modify this document under the terms of the GNU Free Documentation License, Version 1.2 or any later version published by the Free Software Foundation; with no Invariant Sections, with no Front-Cover Texts and with no Back-Cover Texts. A copy of the license is included in the section entitled "GNU Free Documentation License".

If you have questions, please visit the following url: http://www.gnu.org/licenses/fdl.txt and contact at: \htmladdnormallink{blainett@yahoo.es}{mailto://blainett@yahoo.es}

\include{manual_gosa_en_ldap}

\include{manual_gosa_en_apache}

\chapter{GOsa}

\chapter{The Servers}
\label{servers}
\section{Postfix}
\section{Cyrus-IMAP}
\section{Samba 2/3}
\section{Pure-Ftpd}
\section{Squid}
\section{Egroupware}

\bibliography{referencias_gosa}
\bibliographystyle{unsrt}

\end{document}
